% 
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0
% Unported License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-sa/3.0/.
%
% Original authors: Zi Yang <ziy@cs.cmu.edu>, Di Wang <diwang@cs.cmu.edu>
% Original date: 08/28/2013
%
% Edit authors: Avner Maiberg <amaiberg@cs.cmu.edu>
% Edit date: 08/24/2013

\documentclass[oneside]{memoir}

\renewcommand{\chaptername}{Task}

\usepackage{times}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{Task \thesection}{1em}{}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{{../../fig/prerequisites/}}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.95,0.95,1}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=2, 
  numbersep=5pt,
  backgroundcolor=\color{lightblue},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  frame=lines,
  rulecolor=\color{black},
  tabsize=2,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  escapeinside={\%*}{*)},
  morekeywords={*,...},
}
\usepackage{letltxmacro}
\makeatletter
\LetLtxMacro\@@lst@inputlisting\lst@inputlisting
\renewcommand\lst@inputlisting[2][]{%
  \try@listingspath{#2}%
  \if@tempswa
    \typeout{Using \@foundlisting}%
    \@@lst@inputlisting[#1]{\@foundlisting}%
  \else
    \typeout{Missing file #2}\endgroup
  \fi}
\def\listingspath#1{\def\@listingspath{#1}}
\listingspath{}
\def\try@listingspath#1{%
  \@tempswafalse
  \expandafter\@tfor\expandafter\next
  \expandafter:\expandafter=\@listingspath\do
  {\if@tempswa\@break@tfor\fi
   \IfFileExists{\next/#1}{\@tempswatrue\xdef\@foundlisting{\next/#1}}{}}%
}
\makeatletter
\listingspath{{../../lst/prerequisites}}

\definecolor{shadecolor}{gray}{0.9}

\newenvironment{qa}
{\begin{shaded}\begin{itemize}}
{\end{itemize}\end{shaded}}

\title{{\bfseries 11-791 Design and Engineering of Intelligent Information
System \& \\11-693 Software Methods for Biotechnology \\Homework 0}\\
\vspace{1em}
\itshape\rmfamily Software installation, configuration, and your first Maven
project hosted on GitHub}

\date{}

\begin{document}

\begin{titlingpage}
\maketitle

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}
\vspace{-5em}
\textbf{Important dates}
\begin{itemize}

\item \textbf{Hand out: August 27.}

\item \textbf{Turn in: September 8.} A bash script will automatically collect
your submissions and execute your latest release (e.g., hw0-ID-0.0.1.jar) on our
maven repository. The output from your jar will be compared with our expected
output. Simply copying the code from this guideline should work!
\end{itemize}

\textbf{Useful information}
\begin{enumerate}
\item We suggest you to start Homework 0 as early as possible.

\item 
Even though we provide instructions for installing tools on Linux, Windows,
and Mac, we strongly recommend to use Linux.
We will try our
best to help you solve whatever problems you might have, but we also encourage
you, the experts in any of these platforms, to work with us to answer the
questions from your classmates. 
We also strongly encourage you to use Google to find solutions for potential (installation) problems.

\item 
We expect that most of the general communication between the instructor team and students will take place on Piazza
\url{https://piazza.com/class/hyvsubeilei6dd}.
For private questions, e.g., regarding grades, you may contact instructors by e-mail.
Your friendly TAs are:
Avner Maiberg (\href{mailto:amaiberg@andrew.cmu.edu}{\nolinkurl{amaiberg@andrew.cmu.edu}}), 
Parag Argawal (\href{mailto:paraga@andrew.cmu.edu}{\nolinkurl{paraga@andrew.cmu.edu}}), 
Leonid (Leo) Boytsov (\href{mailto:srchvrs@cmu.edu}{\nolinkurl{srchvrs@cmu.edu}}), or 
Xuezi (Manfred) Zhang (\href{mailto:xueziz@andrew.cmu.edu}{\nolinkurl{xueziz@andrew.cmu.edu}}), 

\item Both source files and derived pdf file of this tutorial are publicly
available (yes, \emph{open source}!) on GitHub

\url{http://github.com/amaiberg/software-engineering-preliminary}

which means if you find any errors or easier ways to achieve the same goal,
please feel free to fork the project and send a pull request back to me. Once
your request is confirmed, a newer version will come out immediately to help
other students! Or you can just report an issue at

\url{http://github.com/amaiberg/software-engineering-preliminary/issues}

\end{enumerate}

\end{minipage}
\hspace{-0.1\textwidth}
\end{titlingpage}

\input{account/intro}

\input{config/intro}

\input{project/intro}

\end{document}
