% 
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0
% Unported License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-sa/3.0/.
%
% author: Zi Yang <ziy@cs.cmu.edu>
% date: 09/02/2012
%
\documentclass[oneside]{memoir}

\renewcommand{\chaptername}{Task}

\usepackage{times}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{Task \thesection}{1em}{}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{{../../fig/uml-and-uima/}}

\usepackage{pstricks}
\usepackage{epsfig}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.95,0.95,1}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  basicstyle=\ttfamily\small,
  numbers=left,
  numberstyle=\tiny\color{gray},
  stepnumber=2, 
  numbersep=5pt,
  backgroundcolor=\color{lightblue},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  frame=lines,
  rulecolor=\color{black},
  tabsize=2,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  title=\lstname,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  escapeinside={\%*}{*)},
  morekeywords={*,...},
}
\usepackage{letltxmacro}
\makeatletter
\LetLtxMacro\@@lst@inputlisting\lst@inputlisting
\renewcommand\lst@inputlisting[2][]{%
  \try@listingspath{#2}%
  \if@tempswa
    \typeout{Using \@foundlisting}%
    \@@lst@inputlisting[#1]{\@foundlisting}%
  \else
    \typeout{Missing file #2}\endgroup
  \fi}
\def\listingspath#1{\def\@listingspath{#1}}
\listingspath{}
\def\try@listingspath#1{%
  \@tempswafalse
  \expandafter\@tfor\expandafter\next
  \expandafter:\expandafter=\@listingspath\do
  {\if@tempswa\@break@tfor\fi
   \IfFileExists{\next/#1}{\@tempswatrue\xdef\@foundlisting{\next/#1}}{}}%
}
\makeatletter
\listingspath{{../../lst/uml-and-uima/}}

\usepackage{multirow}

\definecolor{shadecolor}{gray}{0.9}

\newenvironment{qa}
{\begin{shaded}\begin{itemize}}
{\end{itemize}\end{shaded}}

\title{{\bfseries 11-791 Design and Engineering of Intelligent Information
System \& \\11-693 Software Methods for Biotechnology \\Homework 2}\\
\vspace{1em}
\itshape\rmfamily Logical Architecture and UIMA Analysis Engines Design \&
Implementation}

\date{}

\begin{document}

\begin{titlingpage}
\maketitle

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}
\vspace{-5em}
\textbf{Important dates}
\begin{itemize}

\item \textbf{Hand out: September 24.}\footnote{This version was built on \today}

\item \textbf{Turn in: October 8.} In this homework, you will implement the
logical architecture for the sample information processing task from the previous homework:
\emph{Gene Mention Tagging}. Based on a standard type system we give you in
the new archetype, you will need to create analysis engines and annotators to
annotate the sample input files. 

Note that unlike the previous homework, we ask you to implement more than one UIMA annotator.
These annotators will function as a part of an aggregate analysis engine.

You should organize your project in the same
hierarchy as shown below:

\small
\begin{verbatim}
hw2-ID
|- pom.xml
`- src
     `- main
        |- java
      |   `- **/*.java      /* Java classes generated by JCasGen
      |                        and your UIMA annotators         */ 
        `- resources
         |- hw2-ID-aae.xml /* your aggregate analysis engine */
         |- **/*.*                /* analysis engine and other resources */
         `- docs
            `- hw2-ID-report.pdf  /* your report for design */

\end{verbatim}
\normalsize

\end{itemize}

\end{minipage}
\hspace{-0.1\textwidth}

\hspace{-0.1\textwidth}
\begin{minipage}{1.2\textwidth}

Several notes about organizing your Maven project and other additional
information:

\begin{enumerate}

\item \textbf{Submission:} The same way as you did for Homework 0 and 1 (set up
GitHub repo, create Maven project, write your code, submit to Maven repo),
except that the name has changed to hw2-ID.

\item \textbf{Your report for design:} We expect to see how you design the
logical architecture for the sample information system in your report. We will
pull out your documents from your jar files. Remember to include your ID as part
of file names, and put your name and ID in your document. Please submit in PDF
format only.

\item \textbf{Javadocs:} Please remember to give an appropriate description for
each annotator you create.

\item 
We expect that most of the general communication between the instructor team and students will take place on Piazza
\url{https://piazza.com/class/hyvsubeilei6dd}.
For private questions, e.g., regarding grades, you may contact instructors by e-mail.
Your friendly TAs are:
Avner Maiberg (\href{mailto:amaiberg@andrew.cmu.edu}{\nolinkurl{amaiberg@andrew.cmu.edu}}), 
Parag Argawal (\href{mailto:paraga@andrew.cmu.edu}{\nolinkurl{paraga@andrew.cmu.edu}}), 
Leonid (Leo) Boytsov (\href{mailto:srchvrs@cmu.edu}{\nolinkurl{srchvrs@cmu.edu}}), or 
Xuezi (Manfred) Zhang (\href{mailto:xueziz@andrew.cmu.edu}{\nolinkurl{xueziz@andrew.cmu.edu}}), 

\end{enumerate}

\end{minipage}
\hspace{-0.1\textwidth}

\end{titlingpage}

\input{uima/intro}

\input{appendix/intro}

\end{document}
